quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-08 paper-quollr.Rmd
Found the way to fix the issue of selecting, deselecting and add the box

algofig <- bscols(
  htmltools::div(
    style = "
      display: flex;
      justify-content: center;     /* centers the grid horizontally */
      align-items: center;          /* optional: centers vertically if space allows */
      margin: 0 auto;
      padding: 0;
    ",
    htmltools::div(
      style = "
        display: grid;
        grid-template-columns: 1fr 1fr;
        gap: 0px;
        align-items: start;
        justify-items: center;
        margin: 0;
        padding: 0;
      ",
      htmltools::div(style = 'margin: 0; padding: 0;  height: 300px; width: 300px;', hex_grid_poly_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 350px; width: 400px;', hex_centroids_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 300px; width: 300px;', wireframe_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; margin-left: 60px; height: 300px;', scurve_umap_model_vis_n)
    )
  ),
  device = "xs"
)

@@

nldr_plt <- ggplotly(nldr_plt, width = 300,
                     height = 300, tooltip = "none") |>
  style(unselected=list(marker=list(opacity=1))) |>
  highlight(on="plotly_selected", off="plotly_deselect") |>
  config(displayModeBar = FALSE)

>>>>

algofig <- bscols(
  htmltools::div(
    style = "
      display: flex;
      justify-content: center;     /* centers the grid horizontally */
      align-items: center;          /* optional: centers vertically if space allows */
      margin: 0 auto;
      padding: 0;
    ",
    htmltools::div(
      style = "
        display: grid;
        grid-template-columns: 1fr 1fr;
        gap: 0px;
        align-items: start;
        justify-items: center;
        margin: 0;
        padding: 0;
      ",
      htmltools::div(style = 'margin: 0; padding: 0;  height: 300px; width: 370px; text-align: left;', htmltools::h4("a"), hex_grid_poly_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 350px; width: 300px; text-align: left;', htmltools::h4("b"), hex_centroids_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 300px; width: 370px;  text-align: left;', htmltools::h4("c"), wireframe_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 350px; width: 300px; text-align: left;', htmltools::h4("d"), htmltools::div(
    style = "margin-left: 90px;",
    scurve_umap_model_vis_n
  ))
    )
  ),
  device = "xs"
)

@@

nldr_plt <- plot_ly(
    shared_df,
    x = ~emb1, y = ~emb2,
    type = "scatter",
    mode = "markers",
    marker = list(
        color = point_colours[1],
        size = 3,
        opacity = 0.5
    ),
    hoverinfo = "none"
) |>
    layout(
        width = 300,
        height = 300,
        xaxis = list(
            title = "",
            showgrid = FALSE,
            zeroline = FALSE,
            showticklabels = FALSE,
            ticks = "",
            linecolor = "black",
            mirror = TRUE
        ),
        yaxis = list(
            title = "",
            showgrid = FALSE,
            zeroline = FALSE,
            showticklabels = FALSE,
            ticks = "",
            linecolor = "black",
            mirror = TRUE
        ),
        margin = list(l = 20, r = 20, t = 20, b = 20),
        dragmode = "select"
    ) |> 
    style(selected   = list(marker = list(opacity = 1)), unselected=list(marker=list(opacity=1))) |>
    highlight(on="plotly_selected", off="plotly_deselect") |>
    config(displayModeBar = FALSE)
```
